Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-08-04 tensor/draft/draft-tensor-op.tex
[draft] Finish comment, one last todo remains, eos with doi

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and
scalar couplings has been presented in \cite{Bobeth:2007dw,
  Bobeth:2012vn}, adopting the effective theory \refeq{eq:Heff},
i.e. neglecting higher-dimensional operators with {$\mbox{dim} \geq
  8$}. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}
    {\bigg/ \Gamma_\ell} \,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.
The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed {by small
lepton masses for the considered kinematical region $1 \leq q^2 \leq 22$ GeV$^2$}
\cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.
Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher-order QED
corrections, which will modify the simple $\cos\theta_\ell$ dependence of the angular
distribution~\refeq{eq:ang-distr}, however, currently there is no solid estimate
available for this source of SM background\footnote{The \christoph{logarithmically
enhanced NLO QED corrections}
  to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
  corresponding effects in $B\to K \bar\ell\ell$.}. \todo{David's comment?!}

@@

\begin{figure*}
  \setlength{\relwidth}{0.33\textwidth}
  \begin{center}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
    % \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \end{center}
  \caption{ The sensitivity of to the tensor coupling $\mbox{Re}(\wilson{T})$
    of\christoph{: $F_H^\mu$} (first row) and \christoph{${\cal B}_\mu$} (second row)
    in $B^+ \to K^+ \bar\mu\mu$
    \christoph{as well as} \christoph{${\cal B}_\mu$} (third row), $(J_{1c} + J_{2c})$
    (fourth row), and $(J_{1s}-3 J_{2s})$ (fifth row) in $B^0 \to K^{*0} \bar\mu\mu$
    integrated over low- and high-$q^2$ bins. In the last two rows, the observables
    are rescaled by the
    lifetime of the $B$ meson for easier comparison with the branching
    ratios. The bands represent the theory uncertainties at 68\% and 95\%
    probability of the prior predictive distribution.  For comparison, two sets
    of bands are shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
    $\wilson[NP]{9} = -1.1$ (red), and an additional band of the latest 68\%
    confidence interval reported by LHCb (grey) if a measurement is
    available. }
  \label{fig:FHvsCT}
\end{figure*}

@@

Only tensor contributions enter
\begin{align}
  (J_{1s} - 3\, J_{2s}) & \propto
  \left(\ldots |\wilson{T}|^2 + \ldots |\wilson{T5}|^2 \right) \,,
\end{align}
where the dots indicate different kinematic and form-factor dependencies.  But
tensor \emph{and} scalar contributions enter
\begin{equation}
\begin{aligned}
  (J_{1c} + J_{2c}) & \propto
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2 \right)
\\
  & + \ldots \left(|\wilson{S} - \wilson{S'}|^2 + |\wilson{P} - \wilson{P'}|^2 \right) \,,
\end{aligned}
\end{equation}
which is similar to the dependence of $F_H^\ell$ in $B\to K
\bar\ell\ell$
\begin{equation}
  \label{eq:FH-dependence}
\begin{aligned}
  F_H^\ell  \propto & \Big[
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2\right)
\\
  & + \ldots \left(|\wilson{S} + \wilson{S'}|^2 + |\wilson{P} + \wilson{P'}|^2 \right)
  \Big]
  \Big/ \Gamma_\ell \,.
\end{aligned}
\end{equation}
Concerning $F_H^\ell$, the involved kinematic factors---see \cite{Bobeth:2007dw,
  Bobeth:2012vn}---are such that tensor and scalar couplings contribute only
constructively/cumulatively, apart from cancellations among $\wilson{S(P)}$ and
$\wilson{S'(P')}$.  Interference terms in the numerator of $F_H^\ell$ of the
form $(\wilson{T} \times \wilson{7,7',9,9'})$ and $(\wilson{P,P'} \times
\wilson{10,10'})$ are suppressed by $m_\ell/\sqrt{q^2}$. \christoph{They become numerically
relevant in cases $\wilson{T} \ll \wilson{7,7',9,9'}$ or $\wilson{P,P'}
\ll\wilson{10,10'}$, where the smallness of Wilson coefficient is of the
same level as the suppression factor $m_\ell/\sqrt{q^2}$ of the large vectorial
SM Wilson coefficients $\wilson[SM]{9,10}$, which implies however no large
enhancement of $F_H^\ell$ over the SM prediction.}

@@

From \reffig{fig:FHvsCT}, the highest sensitivity to tensor couplings of any $B
\to K$ observable is attained by \christoph{$F_H^\mu$} at high $q^2$ due to a partial
cancellation of form factors \cite{Bobeth:2012vn}. If the experimental
uncertainty could be reduced further, \christoph{$F_H^\mu$} would give a very strong
constraint on a simultaneous negative shift in $\wilson[NP]{9}$ and
\christoph{$\wilson{T}$}. The prediction of \christoph{${\cal B}(B\to K \bar\mu\mu)$} is
essentially insensitive to $\wilson{T}$ but sensitive to \christoph{$\wilson[NP]{9}$}. A
stronger impact on global fits, however, would \christoph{require a} reduced theory
uncertainty.

The observable \christoph{${\cal B}(B\to K^* \bar\mu\mu)$} shows moderate dependence on
$\wilson{T}$ at least at low $q^2$ and has some impact on the constraints on
tensor couplings as will be discussed in \refsec{sec:results}. At the moment,
theory and experimental uncertainty are of similar size.

$(J_{1c}+J_{2c})$ is sensitive to $\wilson{T}$ in both $q^2$ regimes. At low~$q^2$,
it is mildly affected by $\wilson[NP]{9}$, whereas at high $q^2$ it is
unaffected. Regarding $(J_{1s}-3J_{2s})$, the situation is reversed: here the
strong dependence on $\wilson{T}$ appears at low $q^2$.  Overall, \christoph{$F_H^\mu$},
$(J_{1c}+J_{2c})$ at \christoph{high} $q^2$, and $(J_{1s}-3J_{2s})$ are sensitive
to $\wilson{T}$ and theoretically very clean around $\wilson{T}=0$.

From the available measurements, \christoph{$F_H^\mu$} at high $q^2$ currently provides the
most stringent constraints on the size of tensor couplings. Moreover, the
dependence on vector couplings is such that $\wilson[NP]{9} \lesssim 0$ leads to
stronger constraints on~$\wilson{T}$ than $\wilson[NP]{9} \approx
0$.

@@

Eventually we also explore the effect of interference with \christoph{NP contributions}
in the vector couplings $\wilson{9,\,9',\,10,\,10'}$ on the bounds
on tensor and scalar couplings.  For this purpose we include also the branching
ratio, the lepton forward-backward asymmetry, and the rate CP asymmetry of
$B\to K^* \bar\mu\mu$ as they provide additional constraints on the real and
imaginary parts of $\wilson{9,\,9',\,10,\,10'}$. The experimental \christoph{input} of all
observables entering our fits is listed in \reftab{tab:observables} together with input for
the $B\to K^{(*)}$ form factors. More details on the latter can be found in
\refapp{app:theory:inputs}.

@@

There are no discrepancies between the latest measurements for $\ell = \mu$
(throughout this section) of $F_H^\mu$ and $A_{\rm FB}^\mu$ in $B^+ \to K^+
\bar\mu\mu$ and their tiny SM predictions; cf. \reffig{fig:FHvsCT}. Thus our
main objective is to derive constraints on tensor and scalar couplings through
the enhanced sensitivity of both observables to \christoph{these} couplings compared to
vector couplings. For this purpose, we will consider several model-independent
scenarios, progressing from rather restricted to more general ones in order to
asses the effect of cancellations due to interference of various contributions.

For each coupling \christoph{that} we vary in a fit, we remain as general as possible, treat it
as a complex number and use the cartesian parametrization assuming uniform
priors for ease of comparison with previous studies. Specifically, we set
\begin{align}
  \label{eq:wilson-prior}
  \mbox{Re}(\wilson{S,S',P,P',T,T5}) &\in [-1, 1],\nn \mbox{Re}(\wilson{9,9',10,10'}) &\in [-7, 7],
\end{align}
and the same for the imaginary parts. The priors of the nuisance parameters are given in \refapp{app:theory:inputs}.

We start with the scenario of only tensor couplings and see that they are well
constrained by $F_H^\mu$ alone. In a second scenario we consider only scalar
couplings in order to investigate the complementarity of $F_H^\mu$ and $B_s \to
\bar\mu\mu$. Here we find that---for the first time---all complex-valued scalar
couplings can be bounded simultaneously by the combination of both
measurements. Finally we consider as a special scenario the SM augmented by
dimension six operators as an effective theory of new physics below some high
scale $\Lambda_{\rm NP}$ assumed much larger than the typical scale of
electroweak symmetry breaking. In addition, the model contains one scalar
doublet under $SU(2)_L$ as in the SM. For each scenario, we also investigate
interference effects with new physics in vector couplings \christoph{$\wilson{9,9',10,10'}$}. Finally, we conclude
this section with posterior predictions---conditional on all experimental
constraints---of the probable ranges of the not-yet-measured angular observables
\christoph{$J_{6c}$, $(J_{1c}+J_{2c})$ and $(J_{1s} - 3J_{2s}$)}
in $B\to K^*\bar\mu\mu$ and $A_{\Delta\Gamma}$ in $B_s\to\bar\mu\mu$.

@@

In a scenario with only \christoph{complex-valued tensor couplings} $\wilson{T,\, T5}$, the
experimental measurement of $F_H^\mu$ constrains the combination $|\wilson{T}|^2
+ |\wilson{T5}|^2$, up to some small interference of $\wilson{T}$ with vector
couplings $\wilson{7,\,7',\,9,\,9'}$; cf. \refeq{eq:FH-dependence}.  The
according 68\% (95\%) 1D-marginalized probability intervals are listed in the
second column of \reftab{tab:cTT5:1-dimCLs}. From the third column, it is seen
that the constraints become tighter when utilising all observables in
\reftab{tab:observables}, mainly due to the sensitivity of the branching ratio
of $B\to K^{*} \bar\mu\mu$ to tensor couplings (see also
\reffig{fig:FHvsCT}). The latter stronger bounds are driven by the new lattice
results of $B\to K^*$ form factors that predict values above the measured
\christoph{ones}~\cite{Horgan:2013pva}. Since tensor couplings contribute constructively
to ${\cal B}(B\to K^{*}\bar\mu\mu)$, large values are better constrained. In
this scenario with vanishing scalar couplings, current measurements of $A_{\rm
  FB}^\mu(B^+\to K^+\bar\mu\mu)$ barely provide any constraint;
cf.~\refeq{eq:AFB-dependence}.

We also perform a fit with nonzero $\wilson[NP]{9,\,10}$ in order to assess the
robustness of the bounds with respect to interference. Note that $\wilson{7,7'}$
appears in linear combinations with $\wilson{9,9'}$ such that its interference
with tensor and scalar couplings is captured implicitly by allowing new physics
in $\wilson{9,9'}$. Thus we fix $\wilson{7,7'}$ to the SM value without loss of
generality. In this case, $F_H^\mu$ by itself still provides bounds on
$|\wilson{T,\,T5}|$ that are weakened by a factor of two since $F_H^\mu$ does
not pose constraints on $\wilson{9,\,10}$ (in the chosen prior range). Once
additional experimental measurements of \reftab{tab:observables} are taken into
account, the potential destructive effects of new physics in $\wilson{9,\,10}$
become reduced and almost the same constraints on $\wilson{T,\,T5}$ are
recovered, as shown in the last column in \reftab{tab:cTT5:1-dimCLs}. If in
addition we allow $\wilson{S,S',P,P'} \ne 0$ (not shown in
\reftab{tab:cTT5:1-dimCLs}), the credible regions further shrink by about 10\%,
which we attribute to \christoph{the} cumulative effect of $\wilson{S,S',P,P'} \ne 0$ in
$F_H^\ell$; cf. \refeq{eq:FH-dependence}. In summary, the $F_H^\mu$
measurement~\cite{Aaij:2014tfa} of LHCb with 3 fb$^{-1}$ shrinks the previous
bounds \cite{Bobeth:2012vn} on $\wilson{T,\,T5}$ by roughly 50\%.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_0,2}
    % \includegraphics[width=.32\textwidth]{plots/pdf/scSP_Bsmumu,scSP_FH,sc910SP_K_KstarBR_Bsmumu_4,6}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,sc910SP_K_KstarBR_Bsmumu_0,4}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_2,6}
  \end{center}
  \caption{ The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$ from
    only $F_H^\mu$~\christoph{[grey dotted]}, only $\overline{\cal B}(B_s \to
    \bar\mu\mu)$ \christoph{[blue dashed]}, and the combination with all other
    data in \reftab{tab:observables} as well as nonzero
    $\wilson[]{9,\,9',\,10,\, 10'}$ \christoph{[red solid]} at 68\% (darker)
    and 95\% (lighter) probability. The constraints on Re$(\wilson{P} \pm
    \wilson{P'})$ are identical to Re$(\wilson{S} \pm \wilson{S'})$, apart from
    a small translation of the contours by $(+0.2,\, +0.15)$. The SM prediction is
    indicated by the black diamond. \checked{} }
  \label{fig:scalar}
\end{figure*}

@@

In the following we consider a \christoph{scenario consisting
of the SM augmented} by dimension six operators that respect the SM gauge group and are
composed of SM fields only. Such a scenario becomes more and more viable for two
reasons. The first is the discovery of a scalar resonance at the LHC in
agreement with all requirements of the Higgs particle in the SM. The second are
the steadily rising lower bounds on the mass of new particles reported by ATLAS
and CMS in various more or less specific models.

A nonredundant set of dimension-six operators of this effective theory (SM-EFT)
was given in \cite{Grzadkowski:2010es} and the matching to the effective theory
of $\Delta B = 1$ decays \refeq{eq:Heff} at the scale $\mu \sim m_W$ of the
order of the $W$-boson \christoph{mass in~\cite{D'Ambrosio:2002ex}} for vector
couplings $\wilson{7,\,9,\,10}$. The matching of tensor \refeq{eq:tensor:ops}
and scalar \refeq{eq:scalar:ops} operators \cite{Alonso:2014csa} shows that SM
gauge groups in conjunction with the linear representation \todo{Ask Martin,
  Oscar how to correctly phrase this} impose the relations
\begin{align}
  \label{eq:mEFT-constraints}
  \wilson{P}  & = -\wilson{S}\,, &
  \wilson{P'} & = \wilson{S'}\,, &
  \wilson{T}  & = \wilson{T5} = 0
\end{align}
on scalar and pseudo-scalar couplings and require tensor couplings to be
suppressed to the level of dimension-eight operators. In consequence only two
scalar couplings $\wilson{S,\, S'}$ arise that scale as $\sim v^2/\Lambda_{\rm
  NP} \ll 1$ where $v^2$ denotes the scale of electroweak symmetry breaking and
$\Lambda_{\rm NP}$ is the high-energy scale at which new physics \christoph{
is decoupled}.

@@

The SM gauge group does not imply any relation between $\wilson{10}$ and
$\wilson{10'}$, so they are in general additional independent parameters. Here
we find that destructive interference with contributions involving
$\wilson{10,\, 10'}$ does not significantly alter the bounds on $\wilson{S,\,
  S'}$.  The results of two fits are shown in \reffig{fig:scalar:SM-EFT}. In the
first fit, we set $\wilson[NP]{10, 10'} = 0$ and include all constraints on
\christoph{$B \to K \bar\mu\mu$ and $B_s \to \bar\mu\mu$}. In the second fit, we allow
$\wilson[NP]{10, 10'} \ne 0$ and further include all \christoph{$B \to K^* \bar\mu\mu$}
constraints from \reftab{tab:observables}. For both fits, all six 2D marginals
of real and imaginary parts of $\wilson{S}$ vs. $\wilson{S'}$ have nearly
circular contours of equal size that contain the SM point at the 68\% level
except for $\mbox{Re}(\wilson{S})$ vs. $\mbox{Re}(\wilson{S'})$ where it is
within the 95\% credible region. The regions hardly vary between the two fits.

>>>>

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and
scalar couplings has been presented in \cite{Bobeth:2007dw,
  Bobeth:2012vn}, adopting the effective theory \refeq{eq:Heff},
i.e. neglecting higher-dimensional operators with {$\mbox{dim} \geq
  8$}. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}
    {\bigg/ \Gamma_\ell} \,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.
The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed {by
  small lepton masses for the considered kinematical region $1 \leq
  q^2 \leq 22$ GeV$^2$} \cite{Bobeth:2007dw, Bobeth:2011nj,
  Bouchard:2013eph}.  Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$
can be induced by higher-order QED corrections, which will modify the
simple $\cos\theta_\ell$ dependence of the angular
distribution~\refeq{eq:ang-distr}, however, currently there is no
solid estimate available for this source of SM background\footnote{The
  {logarithmically enhanced NLO QED corrections} to $B\to
  X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
  corresponding effects in $B\to K \bar\ell\ell$.}. \todo{David's
  comment?!}

@@

\begin{figure*}
  \setlength{\relwidth}{0.33\textwidth}
  \begin{center}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
    % \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \end{center}
  \caption{ The sensitivity to the tensor coupling
    $\mbox{Re}(\wilson{T})$ of $F_H^\mu$ and {${\cal B}_\mu$} in $B^+
    \to K^+ \bar\mu\mu$ {as well as} {${\cal B}_\mu$},
    $(J_{1c} + J_{2c})$, and $(J_{1s}-3 J_{2s})$ in $B^0 \to K^{*0}
    \bar\mu\mu$. All observables are integrated over $q^2$ bins as
    $\langle \dots \rangle_{[q^2_{\rm min}, q^2_{\rm max}]}$. Angular
    observables are rescaled by the lifetime of the $B$ meson,
    $\tau_B$. The bands represent the theory uncertainties at 68\% and
    95\% probability of the prior predictive.  Two sets of bands are
    shown for $\wilson[NP]{9} = 0$ (blue) and $\wilson[NP]{9} = -1.1$
    (red). If available, the grey band indicates the latest 68\%
    confidence interval reported by LHCb.}
  \label{fig:FHvsCT}
\end{figure*}

@@

Only tensor contributions enter
\begin{align}
  (J_{1s} - 3\, J_{2s}) & \propto
  \left(\ldots |\wilson{T}|^2 + \ldots |\wilson{T5}|^2 \right) \,,
\end{align}
where the dots indicate different kinematic and form-factor dependencies.  But
tensor \emph{and} scalar contributions enter
\begin{equation}
\begin{aligned}
  (J_{1c} + J_{2c}) & \propto
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2 \right)
\\
  & + \ldots \left(|\wilson{S} - \wilson{S'}|^2 + |\wilson{P} - \wilson{P'}|^2 \right) \,,
\end{aligned}
\end{equation}
which is similar to the dependence of $F_H^\ell$ in $B\to K
\bar\ell\ell$
\begin{equation}
  \label{eq:FH-dependence}
\begin{aligned}
  F_H^\ell  \propto & \Big[
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2\right)
\\
  & + \ldots \left(|\wilson{S} + \wilson{S'}|^2 + |\wilson{P} + \wilson{P'}|^2 \right)
  \Big]
  \Big/ \Gamma_\ell \,.
\end{aligned}
\end{equation}
Concerning $F_H^\ell$, the involved kinematic factors---see
\cite{Bobeth:2007dw, Bobeth:2012vn}---are such that tensor and scalar
couplings contribute only constructively/cumulatively, apart from
cancellations among $\wilson{S(P)}$ and $\wilson{S'(P')}$.
Interference terms in the numerator of $F_H^\ell$ of the form
$(\wilson{T} \times \wilson{7,7',9,9'})$ and $(\wilson{P,P'} \times
\wilson{10,10'})$ are suppressed by $m_\ell/\sqrt{q^2}$. They become
numerically relevant in case $\wilson{T} \ll \wilson{7,7',9,9'}$ or
$\wilson{P,P'} \ll\wilson{10,10'}$ where the smallness of
$\wilson{T,P,P'}$ is of the same level as the suppression factor
$m_\ell/\sqrt{q^2}$ accompanying the large vectorial SM Wilson
coefficients $\wilson[SM]{9,10} \sim \pm 4$. This implies, however, no
large enhancement of $F_H^\ell$ over the SM prediction.

@@

From \reffig{fig:FHvsCT}, the highest sensitivity to tensor couplings of any $B
\to K$ observable is attained by {$F_H^\mu$} at high $q^2$ due to a partial
cancellation of form factors \cite{Bobeth:2012vn}. If the experimental
uncertainty could be reduced further, {$F_H^\mu$} would give a very strong
constraint on a simultaneous negative shift in $\wilson[NP]{9}$ and
{$\wilson{T}$}. The prediction of {${\cal B}(B\to K \bar\mu\mu)$} is
essentially insensitive to $\wilson{T}$ but sensitive to {$\wilson[NP]{9}$}. A
stronger impact on global fits, however, would {require a} reduced theory
uncertainty.

The observable {${\cal B}(B\to K^* \bar\mu\mu)$} shows moderate dependence on
$\wilson{T}$ at least at low $q^2$ and has some impact on the constraints on
tensor couplings as will be discussed in \refsec{sec:results}. At the moment,
theory and experimental uncertainty are of similar size.

$(J_{1c}+J_{2c})$ is sensitive to $\wilson{T}$ in both $q^2$ regimes. At low~$q^2$,
it is mildly affected by $\wilson[NP]{9}$, whereas at high $q^2$ it is
unaffected. Regarding $(J_{1s}-3J_{2s})$, the situation is reversed: here the
strong dependence on $\wilson{T}$ appears at low $q^2$.  Overall, {$F_H^\mu$},
$(J_{1c}+J_{2c})$ at {high} $q^2$, and $(J_{1s}-3J_{2s})$ are sensitive
to $\wilson{T}$ and theoretically very clean around $\wilson{T}=0$.

From the available measurements, {$F_H^\mu$} at high $q^2$ currently provides the
most stringent constraints on the size of tensor couplings. Moreover, the
dependence on vector couplings is such that $\wilson[NP]{9} \lesssim 0$ leads to
stronger constraints on~$\wilson{T}$ than $\wilson[NP]{9} \approx
0$.

@@

Eventually we also explore the effect of interference with {NP contributions}
in the vector couplings $\wilson{9,\,9',\,10,\,10'}$ on the bounds
on tensor and scalar couplings.  For this purpose we include also the branching
ratio, the lepton forward-backward asymmetry, and the rate CP asymmetry of
$B\to K^* \bar\mu\mu$ as they provide additional constraints on the real and
imaginary parts of $\wilson{9,\,9',\,10,\,10'}$. The experimental {input} of all
observables entering our fits is listed in \reftab{tab:observables} together with input for
the $B\to K^{(*)}$ form factors. More details on the latter can be found in
\refapp{app:theory:inputs}.

@@

There are no discrepancies between the latest measurements for $\ell = \mu$
(throughout this section) of $F_H^\mu$ and $A_{\rm FB}^\mu$ in $B^+ \to K^+
\bar\mu\mu$ and their tiny SM predictions; cf. \reffig{fig:FHvsCT}. Thus our
main objective is to derive constraints on tensor and scalar couplings through
the enhanced sensitivity of both observables to {these} couplings compared to
vector couplings. For this purpose, we will consider several model-independent
scenarios, progressing from rather restricted to more general ones in order to
asses the effect of cancellations due to interference of various contributions.

For each coupling {that} we vary in a fit, we remain as general as possible, treat it
as a complex number and use the cartesian parametrization assuming uniform
priors for ease of comparison with previous studies. Specifically, we set
\begin{align}
  \label{eq:wilson-prior}
  \mbox{Re}(\wilson{S,S',P,P',T,T5}) &\in [-1, 1],\nn \mbox{Re}(\wilson{9,9',10,10'}) &\in [-7, 7],
\end{align}
and the same for the imaginary parts. The priors of the nuisance parameters are given in \refapp{app:theory:inputs}.

We start with the scenario of only tensor couplings and see that they are well
constrained by $F_H^\mu$ alone. In a second scenario we consider only scalar
couplings in order to investigate the complementarity of $F_H^\mu$ and $B_s \to
\bar\mu\mu$. Here we find that---for the first time---all complex-valued scalar
couplings can be bounded simultaneously by the combination of both
measurements. Finally we consider as a special scenario the SM augmented by
dimension six operators as an effective theory of new physics below some high
scale $\Lambda_{\rm NP}$ assumed much larger than the typical scale of
electroweak symmetry breaking. In addition, the model contains one scalar
doublet under $SU(2)_L$ as in the SM. For each scenario, we also investigate
interference effects with new physics in vector couplings {$\wilson{9,9',10,10'}$}. Finally, we conclude
this section with posterior predictions---conditional on all experimental
constraints---of the probable ranges of the not-yet-measured angular observables
{$J_{6c}$, $(J_{1c}+J_{2c})$ and $(J_{1s} - 3J_{2s}$)}
in $B\to K^*\bar\mu\mu$ and $A_{\Delta\Gamma}$ in $B_s\to\bar\mu\mu$.

@@

In a scenario with only {complex-valued tensor couplings} $\wilson{T,\, T5}$, the
experimental measurement of $F_H^\mu$ constrains the combination $|\wilson{T}|^2
+ |\wilson{T5}|^2$, up to some small interference of $\wilson{T}$ with vector
couplings $\wilson{7,\,7',\,9,\,9'}$; cf. \refeq{eq:FH-dependence}.  The
according 68\% (95\%) 1D-marginalized probability intervals are listed in the
second column of \reftab{tab:cTT5:1-dimCLs}. From the third column, it is seen
that the constraints become tighter when utilising all observables in
\reftab{tab:observables}, mainly due to the sensitivity of the branching ratio
of $B\to K^{*} \bar\mu\mu$ to tensor couplings (see also
\reffig{fig:FHvsCT}). The latter stronger bounds are driven by the new lattice
results of $B\to K^*$ form factors that predict values above the measured
{ones}~\cite{Horgan:2013pva}. Since tensor couplings contribute constructively
to ${\cal B}(B\to K^{*}\bar\mu\mu)$, large values are better constrained. In
this scenario with vanishing scalar couplings, current measurements of $A_{\rm
  FB}^\mu(B^+\to K^+\bar\mu\mu)$ barely provide any constraint;
cf.~\refeq{eq:AFB-dependence}.

We also perform a fit with nonzero $\wilson[NP]{9,\,10}$ in order to assess the
robustness of the bounds with respect to interference. Note that $\wilson{7,7'}$
appears in linear combinations with $\wilson{9,9'}$ such that its interference
with tensor and scalar couplings is captured implicitly by allowing new physics
in $\wilson{9,9'}$. Thus we fix $\wilson{7,7'}$ to the SM value without loss of
generality. In this case, $F_H^\mu$ by itself still provides bounds on
$|\wilson{T,\,T5}|$ that are weakened by a factor of two since $F_H^\mu$ does
not pose constraints on $\wilson{9,\,10}$ (in the chosen prior range). Once
additional experimental measurements of \reftab{tab:observables} are taken into
account, the potential destructive effects of new physics in $\wilson{9,\,10}$
become reduced and almost the same constraints on $\wilson{T,\,T5}$ are
recovered, as shown in the last column in \reftab{tab:cTT5:1-dimCLs}. If in
addition we allow $\wilson{S,S',P,P'} \ne 0$ (not shown in
\reftab{tab:cTT5:1-dimCLs}), the credible regions further shrink by about 10\%,
which we attribute to {the} cumulative effect of $\wilson{S,S',P,P'} \ne 0$ in
$F_H^\ell$; cf. \refeq{eq:FH-dependence}. In summary, the $F_H^\mu$
measurement~\cite{Aaij:2014tfa} of LHCb with 3 fb$^{-1}$ shrinks the previous
bounds \cite{Bobeth:2012vn} on $\wilson{T,\,T5}$ by roughly 50\%.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_0,2}
    % \includegraphics[width=.32\textwidth]{plots/pdf/scSP_Bsmumu,scSP_FH,sc910SP_K_KstarBR_Bsmumu_4,6}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,sc910SP_K_KstarBR_Bsmumu_0,4}
    \includegraphics[width=.325\textwidth]{plots/pdf/scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_2,6}
  \end{center}
  \caption{ The constraints on complex-valued
    $\wilson{S,\,S',\,P,\,P'}$ from only $F_H^\mu$~(grey dotted), only
    $\overline{\cal B}(B_s \to \bar\mu\mu)$ (blue dashed), and the
    combination with all other data in \reftab{tab:observables} as
    well as nonzero $\wilson[]{9,\,9',\,10,\, 10'}$ (red solid) at
    68\% (darker) and 95\% (lighter) probability. The constraints on
    Re$(\wilson{P} \pm \wilson{P'})$ are identical to Re$(\wilson{S}
    \pm \wilson{S'})$, apart from a small translation of the contours
    by $(+0.2,\, +0.15)$. The SM prediction is indicated by the black
    diamond. }
  \label{fig:scalar}
\end{figure*}

@@

In the following we consider a {scenario consisting of the
  SM augmented} by dimension-six operators that respect the SM gauge
group and are composed of SM fields only. Such a scenario becomes more
and more viable for two reasons. The first is the discovery of a
scalar resonance at the LHC in agreement with all requirements of the
Higgs particle in the SM. The second are the steadily rising lower
bounds on the mass of new particles reported by ATLAS and CMS in
various more or less specific models.

A nonredundant set of dimension-six operators of this effective theory (SM-EFT)
was given in \cite{Grzadkowski:2010es} and the matching to the effective theory
of $\Delta B = 1$ decays \refeq{eq:Heff} at the scale $\mu \sim m_W$ of the
order of the $W$-boson {mass in~\cite{D'Ambrosio:2002ex}} for vector
couplings $\wilson{7,\,9,\,10}$. The matching of tensor \refeq{eq:tensor:ops}
and scalar \refeq{eq:scalar:ops} operators \cite{Alonso:2014csa} shows that SM
gauge groups in conjunction with the linear representation \todo{Ask Martin,
  Oscar how to correctly phrase this} impose the relations
\begin{align}
  \label{eq:mEFT-constraints}
  \wilson{P}  & = -\wilson{S}\,, &
  \wilson{P'} & = \wilson{S'}\,, &
  \wilson{T}  & = \wilson{T5} = 0
\end{align}
on scalar and pseudo-scalar couplings and require tensor couplings to be
suppressed to the level of dimension-eight operators. In consequence only two
scalar couplings $\wilson{S,\, S'}$ arise that scale as $\sim v^2/\Lambda_{\rm
  NP} \ll 1$ where $v^2$ denotes the scale of electroweak symmetry breaking and
$\Lambda_{\rm NP}$ is the high-energy scale at which new physics {
is decoupled}.

@@

The SM gauge group does not imply any relation between $\wilson{10}$ and
$\wilson{10'}$, so they are in general additional independent parameters. Here
we find that destructive interference with contributions involving
$\wilson{10,\, 10'}$ does not significantly alter the bounds on $\wilson{S,\,
  S'}$.  The results of two fits are shown in \reffig{fig:scalar:SM-EFT}. In the
first fit, we set $\wilson[NP]{10, 10'} = 0$ and include all constraints on
{$B \to K \bar\mu\mu$ and $B_s \to \bar\mu\mu$}. In the second fit, we allow
$\wilson[NP]{10, 10'} \ne 0$ and further include all {$B \to K^* \bar\mu\mu$}
constraints from \reftab{tab:observables}. For both fits, all six 2D marginals
of real and imaginary parts of $\wilson{S}$ vs. $\wilson{S'}$ have nearly
circular contours of equal size that contain the SM point at the 68\% level
except for $\mbox{Re}(\wilson{S})$ vs. $\mbox{Re}(\wilson{S'})$ where it is
within the 95\% credible region. The regions hardly vary between the two fits.
